---
title: "Figures for Nature Paper"
author: "Johannes Wilhelmus Maria Pullens"
date: "2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, include=FALSE}
# Clear the workspace and load required libraries
rm(list = ls())

library(ggplot2) # Version 3.5.1
library(tidyverse) # Version 2.0.0
library(readxl) # Version 1.4.3
library(lme4) # Version 1.1-35.3
library(emmeans) # Version 1.10.2

base_sizeJP <- 16
```

```{r}
# Load the Yield data from an Excel file
Yield <- readxl::read_excel("DATA/CROP_YIELD/Yield_2023.xlsx", sheet = "all")

# Define the plots to exclude from the dataset and remove them
N <- c("N1","N2","N3","N4","N5","N6","N25","N26","N27","N28","N29","N30")
S <- c("S31","S32","S33","S34","S35","S36","S55","S56","S57","S58","S59","S60")
Yield <- Yield[-which(Yield$Plot %in% N), ]
Yield <- Yield[-which(Yield$Plot %in% S), ]

```

```{r}
# Convert columns to appropriate data types
Yield$PV_setup <- as.factor(Yield$PV_setup)
Yield$Location <- as.factor(Yield$Location)
Yield$Product <- as.factor(Yield$Product)
Yield$Dry_Weight_1ha <- as.numeric(Yield$Dry_Weight_1ha)
Yield$Side <- as.factor(Yield$Side)
Yield$Side <- factor(Yield$Side, levels = c("W", "Mid", "E", "S", "M", "N"))

```

```{r}
# Fit a linear mixed-effects model
LM <- lmer(Dry_Weight_1ha ~ PV_setup * Location * Product + (1 | Plot), data = Yield)
```

Data Preprocessing and Updating PV Setup Column

```{r}
# Remove 'Lupin' product from the dataset
Yield <- Yield[-which(Yield$Product == "Lupin"), ]
```

```{r}
# Update the PV_setup column based on the Location
Yield$PV_setup <- as.character(Yield$PV_setup)
Yield$PV_setup[which(Yield$Location == "Out")] <- "Reference"
Yield$PV_setup <- as.factor(Yield$PV_setup)
```

```{r}
# Rename levels of PV_setup for clarity
levels(Yield$PV_setup) <- c("Vertical", "Tilted south-oriented", "Open field")
```


Fit Linear Model for Updated Dataset

```{r}
# Fit a linear model for the updated dataset
LM <- lm(Dry_Weight_1ha ~ PV_setup * Product, data = Yield)
```

Compute Estimated Marginal Means

```{r}
# Compute and plot estimated marginal means for the new model
emm <- emmeans(LM, list(pairwise ~ PV_setup * Product), adjust = "tukey")
```

Data Preparation for Visualization

```{r}
# Rename columns in the Yield dataset for clarity
names(Yield) <- c("PV Setup", "Location", "Product", "Plot", "Dry weight (t/ha)")

# Reorder the Product factor levels for better visualization
Yield$Product <- factor(Yield$Product, levels = c("Grain", "Straw", "Grass-Clover"))
```

Create Boxplot for Yield Data

```{r}
# Function for formatting y-axis labels
scaleFUN <- function(x) sprintf("%.1f", x)

# Create a boxplot for the entire dataset
Allplot <- ggplot(data = Yield, aes(x = Product, y = `Dry weight (t/ha)`)) +
  geom_boxplot(aes(fill = `PV Setup`)) + 
  scale_fill_manual(values = c("#F98D06", "#1A91FF", "green")) +
  theme_bw(base_size = base_sizeJP) +
  theme(legend.position = "bottom") + 
  scale_y_continuous(limits = c(2, 7), labels = scaleFUN)

Allplot
```


Annotate Grass-Clover Data

```{r}
# Define data frames for Grass-Clover annotations
grassclover <- data.frame(a = c(2.75, 2.75, 3, 3, 3), b = c(6.4, 6.5, 6.5, 6.5, 6.4))
grassclover_1 <- data.frame(a = c(3, 3, 3.25, 3.25, 3.25), b = c(6.6, 6.7, 6.7, 6.7, 6.6))

# Add lines and annotations to the plot
Allplot <- Allplot + 
  geom_line(data = grassclover, aes(x = a, y = b)) +
  geom_line(data = grassclover_1, aes(x = a, y = b)) + 
  annotate("text", x = c(2.875, 3.125), y = c(6.6, 6.8), label = "**", size = 7)

Allplot
```

Load and Clean Grass Data for Further Analysis

```{r}
# Load the Grass data from the Excel file
Grass <- read_excel("DATA/CROP_YIELD/Yield_2023.xlsx", sheet = "Grassclover")
Grass <- subset(Grass, select = c("PV_setup", "Location", "Plot", "Dry_Weight_1ha, 03/07/2023", 
                                  "Dry_Weight_1ha, 14/08/2023", "Dry_Weight_1ha, 21/09/2023"))

# Remove specified plots from the dataset
Grass <- Grass[-which(Grass$Plot %in% N), ]
Grass <- Grass[-which(Grass$Plot %in% S), ]

# Update PV_setup and Location columns
Grass$PV_setup[which(Grass$Location == "Out")] <- "Reference"
Grass$Location[which(Grass$Location == "Out")] <- "Reference"
```

Fit Linear Models for Each Grass Cut and Compute Estimated Marginal Means

```{r}
# First cut
LM <- lm(`Dry_Weight_1ha, 03/07/2023` ~ PV_setup * Location, data = Grass)
emmeans(LM, list(pairwise ~ PV_setup * Location), adjust = "tukey")

# Second cut
LM <- lm(`Dry_Weight_1ha, 14/08/2023` ~ PV_setup * Location, data = Grass)
emmeans(LM, list(pairwise ~ PV_setup * Location), adjust = "tukey")

# Third cut
LM <- lm(`Dry_Weight_1ha, 21/09/2023` ~ PV_setup * Location, data = Grass)
emmeans(LM, list(pairwise ~ PV_setup * Location), adjust = "tukey")
```

Reload and Reformat Grass Data for Further Plotting

```{r}
# Reload and reformat Grass data for further plotting
Grass <- readxl::read_excel("DATA/CROP_YIELD/Yield_2023.xlsx", sheet = "Sheet1")
names(Grass) <- c("PV_setup", "Location", "Product", "Plot", "Dry_Weight_1ha", "Date")
Grass <- Grass[-which(Grass$Plot %in% N), ]
Grass <- Grass[-which(Grass$Plot %in% S), ]
```

```{r}
# Update PV_setup column and rename levels
Grass$PV_setup <- as.character(Grass$PV_setup)
Grass$PV_setup[which(Grass$Location == "Out")] <- "Reference"
Grass$PV_setup <- as.factor(Grass$PV_setup)
levels(Grass$PV_setup) <- c("Vertical", "Tilted south-oriented", "Open field")

# Convert Date to factor and create subsets for each cut date
Grass$Date <- factor(Grass$Date)
a1 <- subset(Grass, Date == "2023-07-03")
a2 <- subset(Grass, Date == "2023-08-14")
a3 <- subset(Grass, Date == "2023-09-21")
levels(a1$PV_setup) <- c("V", "T", "O")
levels(a2$PV_setup) <- c("V", "T", "O")
levels(a3$PV_setup) <- c("V", "T", "O")
```

Plot Grass Data for Each Cut

```{r}
# Plot for the first cut (July 3rd, 2023)
grass_plot1 <- ggplot(data = a1, aes(x = PV_setup, y = Dry_Weight_1ha)) + 
  geom_boxplot(aes(fill = PV_setup), show.legend = FALSE) + 
  scale_fill_manual(values = c("#F98D06", "#1A91FF", "green")) + 
  theme_bw(base_size = base_sizeJP) +  # Set base size for theme
  labs(y = "Dry weight (t/ha)", x = "") +  # Label for y-axis and no label for x-axis
  scale_x_discrete(labels = NULL) +  # Remove x-axis labels
  ylim(1.5, 2.8) +  # Set y-axis limits
  ggtitle("2023-07-03") +  # Title for the plot
  theme(plot.title = element_text(hjust = 0.5))  # Center the plot title

grass_plot1
```

```{r}
# Plot for the second cut (August 14th, 2023)
grass_plot2 <- ggplot(data = a2, aes(x = PV_setup, y = Dry_Weight_1ha)) + 
  geom_boxplot(aes(fill = PV_setup), show.legend = FALSE) + 
  scale_fill_manual(values = c("#F98D06", "#1A91FF", "green")) +  
  theme_bw(base_size = base_sizeJP) +  # Set base size for theme
  labs(y = "Dry weight (t/ha)", x = "") +  # Label for y-axis and no label for x-axis
  scale_x_discrete(labels = NULL) +  # Remove x-axis labels
  ylim(1.5, 2.8) +  # Set y-axis limits
  ggtitle("2023-08-14") +  # Title for the plot
  theme(plot.title = element_text(hjust = 0.5))  # Center the plot title

grass_plot2
```
```{r}
# Plot for the third cut (September 21st, 2023)
grass_plot3 <- ggplot(data = a3, aes(x = PV_setup, y = Dry_Weight_1ha)) + 
  geom_boxplot(aes(fill = PV_setup), show.legend = FALSE) + 
  scale_fill_manual(values = c("#F98D06", "#1A91FF", "green")) + 
  theme_bw(base_size = base_sizeJP) +  # Set base size for theme
  labs(y = "Dry weight (t/ha)", x = "PV Setup") +  # Label for y-axis and x-axis
  ylim(1.5, 2.8) +  # Set y-axis limits
  ggtitle("2023-09-21") +  # Title for the plot
  theme(plot.title = element_text(hjust = 0.5))  # Center the plot title

grass_plot3
```

Add Annotations to the Second Cut Plot

```{r}
# Add lines and annotations to the second cut plot to indicate significance
cut2 <- data.frame(a = c(1, 1, 2, 2, 2), b = c(2.45, 2.55, 2.55, 2.55, 2.45))
cut2_1 <- data.frame(a = c(2, 2, 3, 3, 3), b = c(2.6, 2.7, 2.7, 2.7, 2.6))

# Adding lines and asterisks to indicate significance between the setups
grass_plot2 <- grass_plot2 + 
  geom_line(data = cut2, aes(x = a, y = b)) + 
  geom_line(data = cut2_1, aes(x = a, y = b)) +
  annotate("text", x = c(1.5, 2.5), y = c(2.6, 2.75), label = "*", size = 7)
```

Arrange Grass Plots Vertically

```{r}
# Arrange the three grass plots vertically in one column
right <- ggpubr::ggarrange(grass_plot1, grass_plot2, grass_plot3, ncol = 1, legend = FALSE, heights = 100)
```
Combine Overall Yield Plot with Grass Plots

```{r}
# Combine the overall yield plot (Allplot) with the arranged grass plots
complete_graph <- ggpubr::ggarrange(
  Allplot, right, 
  labels = c("a", "b"), 
  widths = c(3.5, 1.5), 
  common.legend = FALSE, 
  font.label = c(size = base_sizeJP + 1)
)

# Display the final combined graph
complete_graph

```
Save the Combined Plot as a PDF

```{r}
# Save the combined plot to a PDF file
pdf("arrangedplot_corrected04092024.pdf", width = 12, height = 7)
print(complete_graph)
dev.off()
```


























