---
title: "LER_HYPERFARM"
author: "M.K.K. Lindhardt"
output: html_document
date: "2024-08-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##############################################################################################################################
PREPARING SCRIPT
##############################################################################################################################

```{r}
# Remove all objects
rm(list = ls())
```

## Packages to be installed first

```{r Installing the pacman package, warning=FALSE}
# install.packages("pacman")
library(pacman)
```

## Installing at loading packages and libraries needed

```{r Loading other needed packages, warning=FALSE}
suppressWarnings({
  # Loading necessary packages with pacman::p_load
  pacman::p_load(
    ############################################################################
    # Data Manipulation and Visualization
    conflicted,
    tidyverse,       # General data manipulation and visualization package
    dplyr,           # Data exploration and manipulation
    patchwork,       # Combines multiple ggplot2 plots side by side or in a grid
    kableExtra,      # Very simple table generator. 
    gt,              # gt table object when provided with table data
    ############################################################################
    # Data Reading and Cleaning
    readxl,          # Reads Excel files
    here,            # Helps with file path management
    writexl,
    ############################################################################
    # Linear Mixed Models and Statistical Analysis
    lme4,            # Fitting linear and generalized linear mixed-effects models
    lmerTest,        # Testing significance in linear mixed models
    emmeans          # Computes estimated marginal means for specified factors in linear models
  )
})

conflicted::conflict_prefer("filter", "dplyr")
conflicted::conflict_prefer("group_by", "dplyr")
conflicted::conflict_prefer("summarize ", "dplyr")
conflicted::conflict_prefer("summarise", "dplyr")
conflicted::conflict_prefer("mutate", "plyr")
conflicted::conflict_prefer("recode", "dplyr")
conflicted::conflict_prefer("summarize", "dplyr")
```


################
## STEP 1
##############################################################################################################################
## READING YIELD DATA
##############################################################################################################################

```{r}
##############################################################################################################################
# PV data
##############################################################################################################################
pv_data <- read_excel("DATA/LER/PV_PANEL_DATA.xlsx")

# view
glimpse(pv_data)
summary(pv_data)
```

##############################################################################################################################
## YIELD
##############################################################################################################################
##############################################################################################################################

```{r}
##############################################################################################################################
#HyPErFarm
##############################################################################################################################
hyperfarm_2023_yield <- read_excel("DATA/LER/HYPERFARM_YIELD_DATA_2023.xlsx",
                                   sheet = "ALL_CROPS_COMBINED") %>%
  filter(PROJECT == "HYPERFARM")

# view
glimpse(hyperfarm_2023_yield)
summary(hyperfarm_2023_yield)
```

################
## STEP 2
##############################################################################################################################
## DATA CLEANING AND PREPROCESSING
##############################################################################################################################

```{r}
yield_data <- hyperfarm_2023_yield %>%
  # Replace "na" strings with actual NA values
  mutate(across(where(is.character), ~ na_if(.x, "na"))) %>% 
  # Convert columns to appropriate types if necessary
   mutate(
    MAIN_STRIP = as.factor(MAIN_STRIP),
    SUB_STRIP = as.factor(SUB_STRIP),
    PLOT_NO = as.factor(PLOT_NO),
    PV_SETUP = as.factor(PV_SETUP),
    LOCATION = as.factor(LOCATION),
    SUB_STRIP_LOCATION = as.factor(SUB_STRIP_LOCATION),
    PRODUCT = as.factor(PRODUCT),
    CUT = as.factor(CUT),
    DRY_WEIGHT_TON_HA   = as.numeric(DRY_WEIGHT_TON_HA)
    ) %>%
  # Safely create the CUT_DATE column
  mutate(CUT_DATE = if_else(!is.na(CUT_YEAR) & !is.na(CUT_MONTH) & !is.na(CUT_DAY),
                            as.Date(paste(CUT_YEAR, CUT_MONTH, CUT_DAY, sep = "-"), format = "%Y-%m-%d"),
                            as.Date(NA))) %>% 
  # assign the value from PV_SETUP when LOCATION is "BETWEEN_PV" and "REFERENCE" when LOCATION is "OUTSIDE_PV", 
  mutate(SETUP_BETWEEN_PV_vs_REFERENCE = if_else(LOCATION == "BETWEEN_PV", 
                                                 as.character(PV_SETUP), "REFERENCE")) %>% 
  # assign the value "REFERENCE" when LOCATION is "OUTSIDE_PV" and otherwise takes the value from SUP_STRIP_LOCATION
  mutate(SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE = if_else(LOCATION == "OUTSIDE_PV", "REFERENCE", 
                                                              as.character(SUB_STRIP_LOCATION)))

glimpse(yield_data)
```

##############################################################################################################################
Assessing yield data
##############################################################################################################################

```{r}
yield_data %>% 
  group_by(PV_SETUP) %>%
  filter(CROP == "WW") %>% 
  filter(PRODUCT == "Straw") %>% 
  #filter(PV_SETUP == "FIXED_TILTED") %>%
  filter(LOCATION == "OUTSIDE_PV") %>% 
  relocate(DRY_WEIGHT_TON_HA, PV_SETUP, SUB_STRIP_LOCATION, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE) 

yield_data %>% 
  filter(CROP == "WW") %>% 
  group_by(PV_SETUP, PRODUCT) %>%
  relocate(DRY_WEIGHT_TON_HA, PV_SETUP, SUB_STRIP_LOCATION, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE) %>% 
  summarize(
    mean_dry_weight = mean(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    sd_dry_weight = sd(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    median_dry_weight = median(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    count = n(),
    .groups = 'drop'
  )

yield_data %>% 
  filter(CROP == "WW") %>% 
  group_by(LOCATION, PV_SETUP, PRODUCT) %>%
  relocate(DRY_WEIGHT_TON_HA, PV_SETUP, SUB_STRIP_LOCATION, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE) %>% 
  summarize(
    mean_dry_weight = mean(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    sd_dry_weight = sd(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    median_dry_weight = median(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    count = n(),
    .groups = 'drop'
  ) |> 
  arrange(PRODUCT)
```

```{r}
# Calculate the global mean yield for each product based on "OUTSIDE_PV" locations
global_means <- yield_data %>%
  filter(LOCATION == "OUTSIDE_PV") %>%  # Only consider "OUTSIDE_PV" locations
  group_by(PRODUCT) %>%  # Group by product
  summarize(global_mean_dry_weight = mean(DRY_WEIGHT_TON_HA, na.rm = TRUE), .groups = 'drop')  # Calculate global mean

# Join the global mean back to the original dataset
yield_data_with_global_mean <- yield_data %>%
  left_join(global_means, by = "PRODUCT")  # Join the global means by product

# View the updated dataset
yield_data_with_global_mean %>%
  filter(CROP == "WW" & PRODUCT == "Grain") %>%  # Filter for "WW" crop as an example
  select(PRODUCT, PV_SETUP, LOCATION, DRY_WEIGHT_TON_HA, global_mean_dry_weight) |>   # Select relevant columns for display
  filter(LOCATION == "OUTSIDE_PV")

# View the updated dataset
yield_data_with_global_mean %>%
  filter(CROP == "GC") %>%  # Filter for "GC" crop as an example
  select(PRODUCT, PV_SETUP, LOCATION, DRY_WEIGHT_TON_HA, global_mean_dry_weight) |>   # Select relevant columns for display
  filter(LOCATION == "OUTSIDE_PV")
```

##############################################################################################################################
# ASSESSING DIFFERENCE IN 'OPEN-FIELD' YIELD DATA
##############################################################################################################################

```{r}
# Fitting linear mixed model for all crops where product type is included as main factor
lmm_hyperfarm <- lmerTest::lmer(DRY_WEIGHT_TON_HA ~ PV_SETUP + LOCATION + PRODUCT + 
                                  PV_SETUP:LOCATION +
                                  PV_SETUP:PRODUCT +
                                  (1 | SUB_STRIP), 
                                data = yield_data)

# Summary of the linear mixed model
# summary(lmm_hyperfarm)
```

```{r}
# Compute estimated marginal means for the interaction PV_SETUP:LOCATION:PRODUCT
emm_outside_pv <- emmeans(lmm_hyperfarm, 
                          pairwise ~ PV_SETUP | LOCATION * PRODUCT, 
                          adjust = "tukey")

# Summary of the estimated marginal means
summary(emm_outside_pv)

# View the contrasts (pairwise comparisons) specifically for LOCATION = OUTSIDE_PV

# Convert contrasts to a data frame

pairs_grain <- emm_outside_pv$contrasts 
pairs_df_grain <- as.data.frame(pairs_grain) %>% 
  arrange(p.value) %>%
  filter(grepl("Grain", contrast) & 
         grepl("OUTSIDE_PV", contrast))

# pairs_df_grain

# LOCATION = OUTSIDE_PV, PRODUCT = Grain:
#  contrast                  estimate        SE    df t.ratio p.value
#  FIXED_TILTED - VERTICAL -0.3148759 0.6087257 53.29  -0.517  0.6071

# LOCATION = OUTSIDE_PV, PRODUCT = Grass_Clover:
#  contrast                  estimate        SE    df t.ratio p.value
#  FIXED_TILTED - VERTICAL -0.5715562 0.4644859 53.08  -1.231  0.2239

# The analysis reveals no significant difference in yields between the FIXED_TILTED and VERTICAL PV setups at the OUTSIDE_PV location for both Grain and Grass-Clover. Although FIXED_TILTED yields are slightly lower, the differences are not statistically significant, indicating that these variations may be due to random chance rather than the PV setup. This means that using the pooled mean yield for 'open-field' yield of 4.274060 for wheat grain and 5.323072 for grass-clover is justifiable when calculating LER.
```

```{r}
# Prepare data for plotting EMMs
emm_means_df <- as.data.frame(emm_outside_pv$emmeans) %>%
  filter(LOCATION == "OUTSIDE_PV" & PRODUCT %in% c("GRAIN", "GRASS_CLOVER")) |> 
  mutate(
      PV_SETUP = case_when(
        PV_SETUP == "FIXED_TILTED" ~ "SOUTH_ORIENTED",
        PV_SETUP == "VERTICAL" ~ "VERTICAL",
        TRUE ~ NA_character_  # Handle unexpected cases
      ))

pv_sys_colors <- c("REFERENCE" = "darkgreen", "SOUTH_ORIENTED" = "skyblue", "VERTICAL" = "orange")

# Create the EMM plot with custom colors
emm_plot <- ggplot(emm_means_df, aes(x = PV_SETUP, y = emmean, fill = PV_SETUP)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.6) +
  facet_wrap(~ PRODUCT, scales = "free_y") +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2, position = position_dodge(0.6)) +
  scale_fill_manual(values = pv_sys_colors) +
  labs(title = "Estimated Marginal Means for OUTSIDE_PV Yields",
       y = "Estimated Marginal Mean (EMM)",
       x = "PV Setup") +
  theme_minimal() +
  theme(legend.position = "none")

emm_plot
```


##############################################################################################################################
# ASSESSING DIFFERENCE BETWEEN THE SUBSTRIPS BETWEEN PV PANELS AND THEIR DIFFERNCE TO REFERENCE 'OUTSIDE_PV' FOR YIELD DATA
##############################################################################################################################
```{r}
yield_data_lm <- yield_data |> 
  mutate(PV_SETUP = case_when(
      PV_SETUP == "FIXED_TILTED" ~ "SOUTH_ORIENTED",
      PV_SETUP == "VERTICAL" ~ "VERTICAL",
      TRUE ~ NA_character_)) |>   # Handle any other cases if they exist
      mutate(SETUP_BETWEEN_PV_vs_REFERENCE = case_when(
      SETUP_BETWEEN_PV_vs_REFERENCE == "FIXED_TILTED" ~ "SOUTH_ORIENTED",
      SETUP_BETWEEN_PV_vs_REFERENCE == "VERTICAL" ~ "VERTICAL",
      SETUP_BETWEEN_PV_vs_REFERENCE == "REFERENCE" ~ "REFERENCE",
      TRUE ~ NA_character_   )) |>  # Handle any other cases if they exist
  mutate(SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE = ifelse(
    SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE == "MIDDLE" & PV_SETUP == "VERTICAL", "MIDDLE_V", 
    ifelse(SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE == "MIDDLE" & PV_SETUP == "SOUTH_ORIENTED", "MIDDLE_S",
           SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE))) |> 
  relocate(PV_SETUP, SETUP_BETWEEN_PV_vs_REFERENCE, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE, PRODUCT, LOCATION, DRY_WEIGHT_TON_HA) |> glimpse()
```


```{r}
# Fitting linear model for all crop, to investigate the difference between substrips (within PV panels) vs. the reference (outside PV panels),
# where product type included as main factor
# The linear model lm_hyperfarm_substrips_full is formulated to evaluate whether there are significant differences in crop yields between different substrips located within the PV setups (east, center, west for VERTICAL, and north, center, south for FIXED_TILTED) and the reference plots located outside the PV panels (open-field). Specifically, the model tests the null hypothesis (H0) that there is no difference in crop yields between any of the substrip positions within the PV systems and the reference plots.

# Simpler model without interactions
lm_hyperfarm_substrips_simple <- lm(DRY_WEIGHT_TON_HA ~ SETUP_BETWEEN_PV_vs_REFERENCE + SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE + PRODUCT, 
                                    data = yield_data_lm)

# Full model with interactions
lm_hyperfarm_substrips_full <- lm(DRY_WEIGHT_TON_HA ~ SETUP_BETWEEN_PV_vs_REFERENCE + SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE + PRODUCT + 
                                    SETUP_BETWEEN_PV_vs_REFERENCE:SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE +
                                    SETUP_BETWEEN_PV_vs_REFERENCE:PRODUCT, 
                                    data = yield_data_lm)

# Summary of the linear model
# summary(lm_hyperfarm_substrips_full)
```

```{r}
par(mfrow = c(2, 2))
plot(lm_hyperfarm_substrips_full)
```
```{r}
summary(lm_hyperfarm_substrips_full)
```

```{r}
# Comparing models using ANOVA
anova(lm_hyperfarm_substrips_simple, lm_hyperfarm_substrips_full)
```

Based on the linear model "lm_hyperfarm_substrips_full" (see below), the analysis aimed to evaluate differences in crop yields across various substrip locations within our two types of PV setups (SOUTH_ORIENTED and VERTICAL) compared to the reference 'open-field' plots. 
The results demonstrate significant effects of both PV setup and substrip location on yield. Specifically, yields are significantly lower in the SOUTH_ORIENTED setup compared to the 'open-field' reference plots (p-val 0.00389), and even more so in the VERTICAL setup, as compared to the reference 'open-field' (p-val < 0.0001). However, among the substrips, the middle substrip in the VERTICAL setup (MIDDLE_V) and the and the western substrip (WEST) both showed significantly higher yields compared to the reference 'open-field' (p-val 0.01442 and 0.02084 respectively). Interactions between PV setup and product type also affected yields; the interaction between the VERTICAL setup and grass-clover is significant (p-val 0.00297). 
Lastly, the ANOVA comparison of the simple and full models indicates that adding interaction terms improves the model, though not significantly (FFF-statistic p=0.084), suggesting that both substrip location and crop type are critical factors in explaining the crop yield outcomes. This supports the hypothesis that yield variation depends on both positioning within PV setups and crop type.


```{r}
# Calculate the means for each combination of factors
overall_means <- yield_data_lm %>%
  group_by(SETUP_BETWEEN_PV_vs_REFERENCE, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE, PRODUCT) |> 
  relocate(SETUP_BETWEEN_PV_vs_REFERENCE, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE, PRODUCT, LOCATION, DRY_WEIGHT_TON_HA) |> 

    summarise(mean_yield = mean(DRY_WEIGHT_TON_HA, na.rm = FALSE))

overall_means
```
```{r}
count_combinations <- yield_data_lm %>%
  group_by(SETUP_BETWEEN_PV_vs_REFERENCE, PRODUCT, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE) %>%
  summarise(n = n()) %>%
  arrange(n)

count_combinations
```
```{r}
# Interaction means
interaction_means <- yield_data_lm %>%
  group_by(SETUP_BETWEEN_PV_vs_REFERENCE, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE, PRODUCT) |> 
  relocate(SETUP_BETWEEN_PV_vs_REFERENCE, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE, PRODUCT, LOCATION, DRY_WEIGHT_TON_HA) |> 
  summarise(mean_yield = mean(DRY_WEIGHT_TON_HA, na.rm = FALSE))

```

```{r}
# Define the colors for each PV setup
PV_sys_colors <- c(
  "REFERENCE" = "darkgreen", 
  "SOUTH_ORIENTED" = "skyblue", 
  "VERTICAL" = "orange"
)
```

```{r}
# Adjust the factor levels order for SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE
interaction_means$SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE <- factor(
  interaction_means$SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE,
  levels = c("NORTH", "MIDDLE_S", "SOUTH", 
             "REFERENCE",
             "EAST", "MIDDLE_V", "WEST")
)


# Plot interaction plot
interaction_means_plot <- interaction_means |> 
  ggplot(aes(x = SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE, 
             y = mean_yield, color = SETUP_BETWEEN_PV_vs_REFERENCE, group = SETUP_BETWEEN_PV_vs_REFERENCE)) +
    geom_line() +
    geom_point() +
    facet_wrap(~ PRODUCT) +
    labs(title = "Interaction Plot: Yield by Sub-Strip Location and PV Setup",
         x = "Sub-Strip Location",
         y = "Mean Dry Weight per Ha",
         color = "PV Setup") +
  theme_minimal() +
  scale_color_manual(values = PV_sys_colors) +
  scale_fill_manual(values = PV_sys_colors) +
    theme(legend.position = "top",  # Remove legend for simplicity
    axis.text.x = element_text(angle = 45, hjust = 1))  # Angle x-axis labels at 45 degrees

interaction_means_plot
```

```{r}
emm_lm_hyperfarm <- emmeans(object = lm_hyperfarm_substrips_full, 
                            pairwise ~ SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE | SETUP_BETWEEN_PV_vs_REFERENCE * PRODUCT,
                            adjust = "tukey")

emm_lm_hyperfarm

# NOTE: A nesting structure was detected in the fitted model:
#     SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE %in% SETUP_BETWEEN_PV_vs_REFERENCE
```

```{r}
# Extract pairwise comparison results
pairs_lm_hyperfarm <- emm_lm_hyperfarm$contrasts 
pairs_lm_hyperfarm <- as.data.frame(pairs_lm_hyperfarm) %>% 
  arrange(p.value)

# Adjust factor levels for SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE

# Update factor levels for SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE
# Check if the levels you want to set are present in the data
expected_levels <- c("NORTH", "MIDDLE_SOUTH_ORIENTED", "SOUTH", 
                     "REFERENCE", 
                     "EAST", "MIDDLE_V", "WEST")

# Correctly relabel `MIDDLE` according to the SETUP_BETWEEN_PV_vs_REFERENCE column
emm_df_lm_hyperfarm <- as.data.frame(emm_lm_hyperfarm$emmeans)
emm_df_lm_hyperfarm

# Filter out non-estimable rows
emm_df_lm_hyperfarm_filtered <- emm_df_lm_hyperfarm %>%
  filter(!is.na(emmean))  # Keep only rows with estimable emmeans

# Manually update the SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE based on SETUP_BETWEEN_PV_vs_REFERENCE
emm_df_lm_hyperfarm_filtered <- emm_df_lm_hyperfarm_filtered %>%
  mutate(SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE = case_when(
    is.na(SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE) & SETUP_BETWEEN_PV_vs_REFERENCE == "SOUTH_ORIENTED" ~ "MIDDLE_S",
    is.na(SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE) & SETUP_BETWEEN_PV_vs_REFERENCE == "VERTICAL" ~ "MIDDLE_V",
    TRUE ~ as.character(SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE)  # Retain existing non-missing values
  ))

# Convert back to a factor with the desired levels
emm_df_lm_hyperfarm_filtered$SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE <- factor(
  emm_df_lm_hyperfarm_filtered$SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE,
  levels = c("NORTH", "MIDDLE_S", "SOUTH", "REFERENCE", "EAST", "MIDDLE_V", "WEST")
)

# Confirm the relabeling
table(emm_df_lm_hyperfarm_filtered$SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE)
```

```{r}
# Compute overall mean for each SETUP_BETWEEN_PV_vs_REFERENCE and SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE
overall_means <- emm_df_lm_hyperfarm_filtered %>%
  group_by(SETUP_BETWEEN_PV_vs_REFERENCE, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE) %>%
  summarise(overall_mean = mean(emmean, na.rm = TRUE)) %>%
  ungroup()

# Create interaction plot with boxplots, lines, and overall mean lines
emmip_plot <- ggplot(emm_df_lm_hyperfarm_filtered, aes(
    x = SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE,
    y = emmean,
    color = SETUP_BETWEEN_PV_vs_REFERENCE,
    group = interaction(SETUP_BETWEEN_PV_vs_REFERENCE, SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE)  # Ensures lines connect correctly
  )) +
  geom_point(size = 3) +  # Points for each mean
  facet_wrap(~ SETUP_BETWEEN_PV_vs_REFERENCE) +
  geom_boxplot(aes(fill = SETUP_BETWEEN_PV_vs_REFERENCE), alpha = 0.2, width = 0.3, outlier.shape = NA, position = position_dodge(width = 0.5)) +  # Boxplots for each group
  #geom_line(data = overall_means, aes(x = SUB_STRIP_LOCATION_BETWEEN_PV_vs_REFERENCE, y = overall_mean), color = "black", size = 1, linetype = "dashed") + 
  scale_color_manual(values = PV_sys_colors) +
  scale_fill_manual(values = PV_sys_colors) +  # Match boxplot color with line/point color
  labs(
    title = "Interaction Plot: Yield by Sub-Strip Location and PV Setup",
    x = "Sub-Strip Location",
    y = "Mean Dry Weight per Ha",
    color = "PV Setup"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

emmip_plot
```




################
## STEP 3
##############################################################################################################################
## CALCULATE a-LER
##############################################################################################################################
```{r}
# Process yield_data and summarize, then join with pv_data
yield_data |> 
  mutate(
    PV_SETUP_2 = case_when(
      PV_SETUP == "VERTICAL" & LOCATION == "BETWEEN_PV" ~ "VERTICAL_BETWEEN_PV",
      PV_SETUP == "VERTICAL" & LOCATION == "OUTSIDE_PV" ~ "VERTICAL_OUTSIDE_PV",
      PV_SETUP == "SOUTH_ORIENTED" & LOCATION == "BETWEEN_PV" ~ "SOUTH_ORIENTED_BETWEEN_PV",
      PV_SETUP == "SOUTH_ORIENTED" & LOCATION == "OUTSIDE_PV" ~ "SOUTH_ORIENTED_OUTSIDE_PV",
      TRUE ~ NA_character_  # Handle any other cases if they exist
    ),
    # Add a new column to match with PV_SETUP in pv_data
    PV_SETUP_MATCH = case_when(
      PV_SETUP == "VERTICAL" ~ "VERTICAL",
      PV_SETUP == "SOUTH_ORIENTED" ~ "SOUTH_ORIENTED",
      TRUE ~ NA_character_
    )
  ) |> 
  relocate(PV_SETUP_2, DRY_WEIGHT_TON_HA) |> 
  
  # Filter data for "Grain" product
  filter(PRODUCT == "GRAIN") |> 
  
  # Group by the new PV_SETUP_2
  group_by(PV_SETUP_2, PV_SETUP_MATCH) |> 
  
  # Summarize crop yields
  summarise(
    mean_dry_weight = mean(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    sd_dry_weight = sd(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    median_dry_weight = median(DRY_WEIGHT_TON_HA, na.rm = TRUE),
    count = n(),
    .groups = 'drop'
  ) |> 
  
  # Join summarized yield data with pv_data on PV_SETUP_MATCH and PV_SETUP
  inner_join(pv_data, by = c("PV_SETUP_MATCH" = "PV_SETUP")) |> 
  
  # Select relevant columns and remove the temporary PV_SETUP_MATCH
  select(PV_SETUP_2, 
         mean_dry_weight, 
         sd_dry_weight, 
         median_dry_weight, 
         count, 
         GCR, 
         ELECTRICITY_OUTPUT_MWH_HA_YR, 
         EFFECIENCY_KWH_KW, 
         INSTALLED_CAPACITY_KW)
```

```{r}
# Create a dataframe for the REFERENCE scenario
reference_data <- tibble(
  PV_SETUP_2 = "REFERENCE",
  mean_dry_weight = NA_real_,  # No crop yield data for the reference scenario
  GCR = 0.5,
  LL_HA = 0,  # No land loss in the reference scenario
  TOTAL_AREA_OCCUPIED_M2 = 1104,
  ELECTRICITY_KW_M2_YR = 93.47,  # Value based on previous calculations
  ELECTRICITY_OUTPUT_MWH_HA_YR = 935
)

reference_data
```

```{r}
# Preprocess PV data: Rename and adjust PV_SETUP_2
pv_data_preproc <- pv_data %>%
  rename(PV_SETUP_2 = PV_SETUP) %>%
  mutate(
    PV_SETUP_2 = case_when(
      PV_SETUP_2 == "VERTICAL" ~ "VERTICAL_BETWEEN_PV",
      PV_SETUP_2 == "SOUTH_ORIENTED" ~ "SOUTH_ORIENTED_BETWEEN_PV",
      PV_SETUP_2 == "REFERENCE" ~ "REFERENCE",
      TRUE ~ NA_character_  # Handle unexpected cases
    )
  )

pv_data_preproc
```

```{r}
# Function to process yield data for a specific product
process_yield_data <- function(yield_data, pv_data, product_name) {
  
  # Prepare yield data: Modify, filter, group, and summarize
  ready_data <- yield_data %>%
    mutate(
      PV_SETUP_2 = case_when(
        PV_SETUP == "VERTICAL" & LOCATION == "BETWEEN_PV" ~ "VERTICAL_BETWEEN_PV",
        PV_SETUP == "VERTICAL" & LOCATION == "OUTSIDE_PV" ~ "VERTICAL_OUTSIDE_PV",
        PV_SETUP == "SOUTH_ORIENTED" & LOCATION == "BETWEEN_PV" ~ "SOUTH_ORIENTED_BETWEEN_PV",
        PV_SETUP == "SOUTH_ORIENTED" & LOCATION == "OUTSIDE_PV" ~ "SOUTH_ORIENTED_OUTSIDE_PV",
        TRUE ~ NA_character_  # Handle unexpected cases
      )
    ) %>%
    filter(PRODUCT == product_name) %>%  # Filter for the specified product
    group_by(PV_SETUP_2) %>%  # Group by the newly created PV_SETUP_2
    summarise(
      mean_dry_weight = mean(DRY_WEIGHT_TON_HA , na.rm = TRUE),
      sd_dry_weight = sd(DRY_WEIGHT_TON_HA , na.rm = TRUE),
      median_dry_weight = median(DRY_WEIGHT_TON_HA , na.rm = TRUE),
      count = n()
    ) %>%
    left_join(pv_data, by = "PV_SETUP_2") %>%  # Merge with PV data
    select(PV_SETUP_2, mean_dry_weight, GCR, LL_HA, 
           TOTAL_AREA_OCCUPIED_M2, ELECTRICITY_KW_M2_YR, 
           ELECTRICITY_OUTPUT_MWH_HA_YR)  # Select relevant columns
  
  # Combine yield data with reference data
  combined_ler_data <- bind_rows(ready_data, reference_data)
  
  return(combined_ler_data)
}
```

```{r}
# Example usage for Grain and Grass-Clover
combined_ler_data_grain <- process_yield_data(yield_data, pv_data_preproc, "GRAIN")
combined_ler_data_clover <- process_yield_data(yield_data, pv_data_preproc, "GRASS_CLOVER")
```
```{r}
calculate_a_LER <- function(combined_ler_data, use_global_mean = FALSE) {
  
  # Calculate the global mean dry weight from all "OUTSIDE_PV" setups
  global_mean_dry_weight <- combined_ler_data %>%
    filter(grepl("OUTSIDE_PV", PV_SETUP_2)) %>%
    summarize(global_mean = mean(mean_dry_weight, na.rm = TRUE)) %>%
    pull(global_mean)
  
  pv_setup_ler <- combined_ler_data %>%
    
    # Calculate the crop yield ratio directly
    mutate(
      crop_yield_ratio = case_when(
        # South-Oriented setup calculation
        PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV" ~ mean_dry_weight / 
          ifelse(use_global_mean, 
                 global_mean_dry_weight,  # Use global mean dry weight as the reference
                 combined_ler_data$mean_dry_weight[combined_ler_data$PV_SETUP_2 == "SOUTH_ORIENTED_OUTSIDE_PV"]  # Use specific mean dry weight
          ),
        # Vertical setup calculation
        PV_SETUP_2 == "VERTICAL_BETWEEN_PV" ~ mean_dry_weight / 
          ifelse(use_global_mean, 
                 global_mean_dry_weight,  # Use global mean dry weight as the reference
                 combined_ler_data$mean_dry_weight[combined_ler_data$PV_SETUP_2 == "VERTICAL_OUTSIDE_PV"]  # Use specific mean dry weight
          ),
        TRUE ~ NA_real_
      ),
      
      # Calculate the land adjustment factor
      land_adjustment_factor = case_when(
        PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV" ~ ((TOTAL_AREA_OCCUPIED_M2 / 10000 - LL_HA) / (TOTAL_AREA_OCCUPIED_M2 / 10000)),
        PV_SETUP_2 == "VERTICAL_BETWEEN_PV" ~ ((TOTAL_AREA_OCCUPIED_M2 / 10000 - LL_HA) / (TOTAL_AREA_OCCUPIED_M2 / 10000)),
        TRUE ~ 1
      ),
      
      # Calculate the crop yield component
      crop_yield_component = crop_yield_ratio * land_adjustment_factor
    ) %>%
    
    # Calculate the energy output component
    mutate(
      energy_output_component = ELECTRICITY_OUTPUT_MWH_HA_YR / combined_ler_data$ELECTRICITY_OUTPUT_MWH_HA_YR[combined_ler_data$PV_SETUP_2 == "REFERENCE"]
    ) %>%
    
    # Calculate a-LER (directly, without percentage adjustments)
    mutate(
      a_LER = crop_yield_component + energy_output_component
    )
  
  return(pv_setup_ler)
}

```

  # Remove all rows with "_OUTSIDE_PV" in the PV_SETUP_2 column
    filter(!grepl("_OUTSIDE_PV", PV_SETUP_2))

```{r}
# Apply the function to both grain and clover datasets

###########################################################################################################
# Wheat grain

a_LER_grain_global_mean <- calculate_a_LER(combined_ler_data = combined_ler_data_grain,
                               use_global_mean = TRUE) |> 
  relocate(PV_SETUP_2, mean_dry_weight, LL_HA, ELECTRICITY_OUTPUT_MWH_HA_YR, a_LER)

  
#############################
a_LER_grain_pv_sys_mean <- calculate_a_LER(combined_ler_data = combined_ler_data_grain,
                               use_global_mean = FALSE) |> 
  relocate(PV_SETUP_2, mean_dry_weight, LL_HA, ELECTRICITY_OUTPUT_MWH_HA_YR, a_LER)

###########################################################################################################
# Grass-clover

a_LER_clover_global_mean <- calculate_a_LER(combined_ler_data = combined_ler_data_clover,
                               use_global_mean = TRUE) |> 
  relocate(PV_SETUP_2, mean_dry_weight, LL_HA, ELECTRICITY_OUTPUT_MWH_HA_YR, a_LER)
#############################
a_LER_clover_pv_sys_mean <- calculate_a_LER(combined_ler_data = combined_ler_data_clover,
                               use_global_mean = FALSE) |> 
  relocate(PV_SETUP_2, mean_dry_weight, LL_HA, ELECTRICITY_OUTPUT_MWH_HA_YR, a_LER)
```

```{r}
# Function to Rename PV_SETUP_2 Values
rename_pv_setup <- function(data) {
  data %>%
    mutate(
      PV_SETUP_2 = case_when(
        PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV" ~ "SOUTH-ORIENTED",
        PV_SETUP_2 == "VERTICAL_BETWEEN_PV" ~ "VERTICAL",
        PV_SETUP_2 == "REFERENCE" ~ "REFERENCE",  # Keep REFERENCE unchanged
        TRUE ~ PV_SETUP_2  # Leave other values unchanged if any
      )
    )
}

# Renaming data valuese:
a_LER_grain_global_mean_clean <- rename_pv_setup(a_LER_grain_global_mean)
a_LER_clover_global_mean_clean <- rename_pv_setup(a_LER_clover_global_mean)

a_LER_grain_pv_sys_mean_clean <- rename_pv_setup(a_LER_grain_pv_sys_mean)
a_LER_clover_pv_sys_mean_clean <- rename_pv_setup(a_LER_clover_pv_sys_mean)
```

```{r}
# View datasets

##################################### Global mean
a_LER_grain_global_mean_clean
a_LER_clover_global_mean_clean
##################################### PV System mean

a_LER_grain_pv_sys_mean_clean
a_LER_clover_pv_sys_mean_clean
```



################
## STEP 4
##############################################################################################################################
## VISUALISE a-LER (PLOTS AND GRAPH)
##############################################################################################################################




```{r}
# Function to Plot a-LER with Custom Colors
plot_a_LER <- function(data) {
  ggplot(data %>% filter(!is.na(a_LER)), aes(x = PV_SETUP_2, y = a_LER, fill = PV_SETUP_2)) +
    geom_bar(stat = "identity") +
    labs(title = "Land Equivalent Ratio (LER)", 
         x = "PV Setup", 
         y = "LER") +
    scale_fill_manual(values = treatment_colors) +  # Apply custom colors
    theme_minimal() +
    theme(legend.position = "none",  # Remove legend for simplicity
    axis.text.x = element_text(angle = 45, hjust = 1))  # Angle x-axis labels at 45 degrees
}

# Function to Plot Crop Yield Component of a-LER with Custom Colors
plot_crop_yield_component <- function(data) {
  ggplot(data %>% filter(!is.na(crop_yield_component)), aes(x = PV_SETUP_2, y = crop_yield_component, fill = PV_SETUP_2)) +
    geom_bar(stat = "identity") +
    labs(title = "Crop Yield Component of LER", 
         x = "PV Setup", 
         y = "Crop Yield Component") +
    scale_fill_manual(values = treatment_colors) +  # Apply custom colors
    theme_minimal() +
    theme(legend.position = "none",  # Remove legend for simplicity
    axis.text.x = element_text(angle = 45, hjust = 1))  # Angle x-axis labels at 45 degrees
}

# Function to Plot Energy Output Component of a-LER with Custom Colors
plot_energy_output_component <- function(data) {
  ggplot(data %>% filter(!is.na(energy_output_component)), aes(x = PV_SETUP_2, y = energy_output_component, fill = PV_SETUP_2)) +
    geom_bar(stat = "identity") +
    labs(title = "Energy Output Component of LER", 
         x = "PV Setup", 
         y = "Energy Output Component") +
    scale_fill_manual(values = treatment_colors) +  # Apply custom colors
    theme_minimal() +
    theme(legend.position = "none",  # Remove legend for simplicity
    axis.text.x = element_text(angle = 45, hjust = 1))  # Angle x-axis labels at 45 degrees
}

# Function to Combine Plots into a Multiplot Layout
plot_combined_a_LER <- function(data, product_type) {
  p1 <- plot_a_LER(data)
  p2 <- plot_crop_yield_component(data)
  p3 <- plot_energy_output_component(data)
  
  # Combine plots with patchwork
  combined_plot <- (p1 | p2 | p3) + 
    plot_annotation(title = paste("LER Analysis for", product_type),
                    theme = theme(plot.title = element_text(size = 20))) + 
    plot_layout(guides = 'collect') & theme(legend.position = 'none')
  
  return(combined_plot)
}
```

```{r}
# Define the color mapping based on the exact values in PV_SETUP_2
treatment_colors <- c(
  "REFERENCE" = "darkgreen", 
  "SOUTH-ORIENTED" = "skyblue", 
  "VERTICAL" = "orange"
)
```

```{r}
# Generate the combined plot for Grain
a_LER_grain_plot_global_mean <- plot_combined_a_LER(a_LER_grain_global_mean_clean, "GRAIN")
a_LER_grain_plot_global_mean
```

```{r, eval=FALSE}
# Specify the folder path and file name
folder_path <- "OUTPUT"
file_name <- "a_LER_grain_plot_global_mean.jpg"
output_path <- file.path(folder_path, file_name)


ggsave(output_path, 
       plot = a_LER_grain_plot_global_mean,
       width = 12, height = 8, dpi = 400)
```



```{r}
# Generate the combined plot for Grass-Clover
a_LER_clover_plot_global_mean <- plot_combined_a_LER(a_LER_clover_global_mean_clean, "GRASS_CLOVER")
a_LER_clover_plot_global_mean
```

```{r}
# Specify the folder path and file name
folder_path <- "OUTPUT"
file_name <- "a_LER_clover_plot_global_mean.jpg"
output_path <- file.path(folder_path, file_name)


ggsave(output_path, 
       plot = a_LER_clover_plot_global_mean,
       width = 12, height = 8, dpi = 400)
```


################
## STEP 5
##############################################################################################################################
## CREATE TABLE OF SUMMARISED a-LER 
##############################################################################################################################

```{r}
# Combine the two datasets for comparison

############################################################################################################
# GLOBAL MEAN
####################################
combined_a_LER_global_mean <- bind_rows(
  a_LER_grain_global_mean %>% mutate(Product = "GRAIN"),
  a_LER_clover_global_mean %>% mutate(Product = "GRASS_CLOVER")
)

############################################################################################################
# PV SETUP-SPECIFIC MEAN
####################################
combined_a_LER_pv_sys <- bind_rows(
  a_LER_grain_pv_sys_mean %>% mutate(Product = "GRAIN"),
  a_LER_grain_pv_sys_mean %>% mutate(Product = "GRASS_CLOVER")
)
```



```{r}
# Select relevant columns for the summary table
summary_table_global_mean <- combined_a_LER_global_mean %>%
  select(Product, PV_SETUP_2, a_LER, crop_yield_ratio, land_adjustment_factor, energy_output_component) %>%
  arrange(Product, PV_SETUP_2) %>%
  kable(format = "html", col.names = c("Product", "PV Setup", "LER", "Crop Yield Ratio", "Land Adjustment Factor", "Energy Output Component")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "center") %>%
  row_spec(0, bold = TRUE, color = "white", background = "#4CAF50")  # Add some style to the header row

# View the summary table in the RStudio viewer
summary_table_global_mean
```


```{r}
# Filter out rows with NA in the a_LER column
filtered_a_LER_global_mean <- combined_a_LER_global_mean %>%
  filter(!is.na(a_LER))

# Create the summary table excluding NA values in a_LER
summary_table_filtered_global_mean <- filtered_a_LER_global_mean %>%
  select(Product, PV_SETUP_2, a_LER, crop_yield_ratio, land_adjustment_factor, energy_output_component) %>%
  arrange(Product, PV_SETUP_2) %>%
  kable(format = "html", col.names = c("Product", "PV Setup", "LER", "Crop Yield Ratio", "Land Adjustment Factor", "Energy Output Component")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, position = "center") %>%
  row_spec(0, bold = TRUE, color = "white", background = "#4CAF50")  # Add some style to the header row

# View the summary table in the RStudio viewer
summary_table_filtered_global_mean
```


##############################################################################################################################
## ADDING RELATIVE CROP AND ENERGY YIELDS
##############################################################################################################################



```{r}
  global_means <- combined_a_LER_global_mean  |> 
    filter(grepl("OUTSIDE_PV", PV_SETUP_2)) %>%
    group_by(Product) %>%
    summarize(global_mean_dry_weight = mean(mean_dry_weight, na.rm = TRUE), .groups = 'drop')

global_means
```



```{r}
add_relative_yield_columns <- function(data, use_global_mean = FALSE) {
  
  # Calculate the global mean yield for each product based on "OUTSIDE_PV" locations
  global_means <- data %>%
    filter(grepl("_OUTSIDE_PV$", PV_SETUP_2)) %>%
    group_by(Product) %>%
    summarise(global_mean_dry_weight = mean(mean_dry_weight, na.rm = TRUE), .groups = 'drop')
  
  # Calculate PV system-specific mean yields for each product based on "OUTSIDE_PV" locations
  pv_system_means <- data %>%
    filter(grepl("_OUTSIDE_PV$", PV_SETUP_2)) %>%
    group_by(Product, PV_SETUP_2) %>%
    summarise(pv_system_mean_dry_weight = mean(mean_dry_weight, na.rm = TRUE), .groups = 'drop')
  
  # Join reference yields to data
  data <- data %>%
    left_join(global_means, by = "Product") %>%
    left_join(pv_system_means, by = c("Product", "PV_SETUP_2"))
  
  # Calculate relative yields separately for GRAIN and GRASS_CLOVER
  data %>%
    mutate(
      # For GRAIN: Calculate relative crop yield for vertical and south-oriented setups
      relative_crop_yield_vertical = ifelse(
        Product == "GRAIN" & PV_SETUP_2 == "VERTICAL_BETWEEN_PV",
        (mean_dry_weight / ifelse(
          use_global_mean, 
          global_means$global_mean_dry_weight[global_means$Product == "GRAIN"], 
          pv_system_means$pv_system_mean_dry_weight[pv_system_means$Product == "GRAIN" & pv_system_means$PV_SETUP_2 == "VERTICAL_OUTSIDE_PV"]
        )) * 100,
        NA_real_
      ),
      
      relative_crop_yield_south_oriented = ifelse(
        Product == "GRAIN" & PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV",
        (mean_dry_weight / ifelse(
          use_global_mean, 
          global_means$global_mean_dry_weight[global_means$Product == "GRAIN"], 
          pv_system_means$pv_system_mean_dry_weight[pv_system_means$Product == "GRAIN" & pv_system_means$PV_SETUP_2 == "SOUTH_ORIENTED_OUTSIDE_PV"]
        )) * 100,
        NA_real_
      ),
      
      # For GRASS_CLOVER: Calculate relative crop yield for vertical and south-oriented setups
      relative_crop_yield_vertical = ifelse(
        Product == "GRASS_CLOVER" & PV_SETUP_2 == "VERTICAL_BETWEEN_PV",
        (mean_dry_weight / ifelse(
          use_global_mean, 
          global_means$global_mean_dry_weight[global_means$Product == "GRASS_CLOVER"], 
          pv_system_means$pv_system_mean_dry_weight[pv_system_means$Product == "GRASS_CLOVER" & pv_system_means$PV_SETUP_2 == "VERTICAL_OUTSIDE_PV"]
        )) * 100,
        relative_crop_yield_vertical  # Retain already calculated values for GRAIN
      ),
      
      relative_crop_yield_south_oriented = ifelse(
        Product == "GRASS_CLOVER" & PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV",
        (mean_dry_weight / ifelse(
          use_global_mean, 
          global_means$global_mean_dry_weight[global_means$Product == "GRASS_CLOVER"], 
          pv_system_means$pv_system_mean_dry_weight[pv_system_means$Product == "GRASS_CLOVER" & pv_system_means$PV_SETUP_2 == "SOUTH_ORIENTED_OUTSIDE_PV"]
        )) * 100,
        relative_crop_yield_south_oriented  # Retain already calculated values for GRAIN
      ),
      
      # Calculate relative energy yield for vertical and south-oriented setups
      relative_energy_yield_vertical = ifelse(
        PV_SETUP_2 == "VERTICAL_BETWEEN_PV",
        (ELECTRICITY_OUTPUT_MWH_HA_YR / data$ELECTRICITY_OUTPUT_MWH_HA_YR[data$PV_SETUP_2 == "REFERENCE"]) * 100,
        NA_real_
      ),
      
      relative_energy_yield_south_oriented = ifelse(
        PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV",
        (ELECTRICITY_OUTPUT_MWH_HA_YR / data$ELECTRICITY_OUTPUT_MWH_HA_YR[data$PV_SETUP_2 == "REFERENCE"]) * 100,
        NA_real_
      ),
      
      # Calculate land loss percentages for vertical setups
      land_loss_vertical = ifelse(
        PV_SETUP_2 == "VERTICAL_BETWEEN_PV",
        (LL_HA / (TOTAL_AREA_OCCUPIED_M2 / 10000)) * 100,
        NA_real_
      ),
      
      # Calculate land loss percentages for south-oriented setups
      land_loss_south_oriented = ifelse(
        PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV",
        (LL_HA / (TOTAL_AREA_OCCUPIED_M2 / 10000)) * 100,
        NA_real_
      )
    )
}

```


Apply the function to the combined_a_LER dataset

```{r}
############################################################################################################
# GLOBAL MEAN
####################################
# Calculate relative yields using the global mean as the reference
combined_a_LER_relative_yield_global_mean <- add_relative_yield_columns(
  data = combined_a_LER_global_mean,
  use_global_mean = TRUE
)

# Select and view the relevant columns for the global mean calculation
combined_a_LER_relative_yields_global_mean_table <- combined_a_LER_relative_yield_global_mean %>%
  select(PV_SETUP_2, Product, a_LER, mean_dry_weight, ELECTRICITY_OUTPUT_MWH_HA_YR, 
         relative_crop_yield_vertical, relative_crop_yield_south_oriented, 
         relative_energy_yield_vertical, relative_energy_yield_south_oriented, 
         land_loss_vertical, land_loss_south_oriented)

# Display the global mean table
combined_a_LER_relative_yields_global_mean_table


############################################################################################################
# PV SETUP-SPECIFIC MEAN
####################################
# Calculate relative yields using PV setup-specific means as the reference

```

```{r}
combined_a_LER_relative_yield_global_mean |> glimpse()
```


```{r}
# Function to create clean and ordered product tables with space instead of NA and reduced digits
create_clean_product_table <- function(data, product_name) {
  data %>%
    filter(Product == product_name & !grepl("_OUTSIDE_PV", PV_SETUP_2)) %>%  # Filter by product and exclude _OUTSIDE_PV rows
    mutate(
      # Combine relative crop yields into one column
      relative_crop_yield = case_when(
        grepl("VERTICAL", PV_SETUP_2) ~ relative_crop_yield_vertical,
        grepl("SOUTH_ORIENTED", PV_SETUP_2) ~ relative_crop_yield_south_oriented,
        TRUE ~ NA_real_
      ),
      # Combine relative energy yields into one column
      relative_energy_yield = case_when(
        grepl("VERTICAL", PV_SETUP_2) ~ relative_energy_yield_vertical,
        grepl("SOUTH_ORIENTED", PV_SETUP_2) ~ relative_energy_yield_south_oriented,
        TRUE ~ NA_real_
      ),
      # Combine land loss into one column
      land_loss = case_when(
        grepl("VERTICAL", PV_SETUP_2) ~ land_loss_vertical,
        grepl("SOUTH_ORIENTED", PV_SETUP_2) ~ land_loss_south_oriented,
        TRUE ~ NA_real_
      ),
      # Replace NA with space character and format numbers to 3 decimal places
      across(c(a_LER, relative_crop_yield, relative_energy_yield, land_loss, mean_dry_weight, ELECTRICITY_OUTPUT_MWH_HA_YR), 
             ~ ifelse(is.na(.), " ", format(round(., 2), nsmall = 2)))
    ) %>%
    select(
      PV_SETUP_2, a_LER, relative_crop_yield, relative_energy_yield, 
      land_loss, mean_dry_weight, ELECTRICITY_OUTPUT_MWH_HA_YR
    ) %>%
    kable(
      format = "html",
      col.names = c(
        "PV Setup", "LER", "Relative Crop Yield (%)", "Relative Energy Yield (%)", 
        "Land Loss (%)", "Mean Dry Weight (t/ha)", "Electricity Output (MWh/ha/yr)"
      ),
      caption = paste("Relative Yields, a_LER, and Land Loss for", product_name)
    ) %>%
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed", "responsive"),
      full_width = F, position = "center"
    ) %>%
    row_spec(0, bold = TRUE, color = "white", background = "#4CAF50")  # Add style to the header row
}
```

```{r}
# Create tables for Grass-Clover and Wheat (Grain)
clean_wheat_grain_table_global_mean <- create_clean_product_table(combined_a_LER_relative_yields_global_mean_table, "GRAIN")
clean_grass_clover_table_global_mean <- create_clean_product_table(combined_a_LER_relative_yields_global_mean_table, "GRASS_CLOVER")
```

```{r}
# Display the tables
combined_a_LER_relative_yields_global_mean_table |> glimpse()
```


##############################################################################################################################
gt table for paper
##############################################################################################################################


##########################################################
GLOBAL MEAN _OUTSIDE_PV YIELD AS 'OPEN-FIELD' REFERENCE
##########################################################

```{r}
# Create combined columns for relative yields and land loss
combined_a_LER_relative_yields_for_table_global_mean <- combined_a_LER_relative_yields_global_mean_table %>%
  mutate(
    relative_crop_yield = ifelse(!is.na(relative_crop_yield_vertical), relative_crop_yield_vertical, relative_crop_yield_south_oriented),
    relative_energy_yield = ifelse(!is.na(relative_energy_yield_vertical), relative_energy_yield_vertical, relative_energy_yield_south_oriented),
    land_loss = ifelse(!is.na(land_loss_vertical), land_loss_vertical, land_loss_south_oriented)
  )

# Filter and prepare data for "GRAIN"
grain_data_global_mean <- combined_a_LER_relative_yields_for_table_global_mean %>%
  filter(Product == "GRAIN", 
         !grepl("_OUTSIDE_PV", PV_SETUP_2)) %>%  # Exclude "_OUTSIDE_PV" rows
    mutate(
      PV_SETUP_2 = case_when(
        PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV" ~ "Tilted south-oriented",
        PV_SETUP_2 == "VERTICAL_BETWEEN_PV" ~ "Vertical",
        PV_SETUP_2 == "REFERENCE" ~ "REFERENCE",  # Keep REFERENCE unchanged
        TRUE ~ PV_SETUP_2  # Leave other values unchanged if any
      )
    ) |> 
  select(
    PV_SETUP_2,
    a_LER,
    relative_crop_yield,
    relative_energy_yield,
    land_loss,
    mean_dry_weight,
    ELECTRICITY_OUTPUT_MWH_HA_YR
  )


# Filter and prepare data for "GRASS_CLOVER"
clover_data_global_mean <- combined_a_LER_relative_yields_for_table_global_mean %>%
  filter(Product == "GRASS_CLOVER", 
         !grepl("_OUTSIDE_PV", PV_SETUP_2)) %>%  # Exclude "_OUTSIDE_PV" rows
  mutate(
      PV_SETUP_2 = case_when(
        PV_SETUP_2 == "SOUTH_ORIENTED_BETWEEN_PV" ~ "Tilted south-oriented",
        PV_SETUP_2 == "VERTICAL_BETWEEN_PV" ~ "Vertical",
        PV_SETUP_2 == "REFERENCE" ~ "REFERENCE",  # Keep REFERENCE unchanged
        TRUE ~ PV_SETUP_2  # Leave other values unchanged if any
      )
    ) |> 
  select(
    PV_SETUP_2,
    a_LER,
    relative_crop_yield,
    relative_energy_yield,
    land_loss,
    mean_dry_weight,
    ELECTRICITY_OUTPUT_MWH_HA_YR
  )

```



```{r, warning=FALSE}
##################################################################################################################

# Customize the grain table
grain_table_global_mean <- grain_data_global_mean %>%
  mutate(a_LER = (a_LER * 100) - 100) %>%  # Convert a-LER to percentage
  filter(!c(PV_SETUP_2 == "REFERENCE")) %>%  # Exclude the relative_energy_yield row
  gt() %>%
  tab_header(
    title = "Winter Wheat Grain"
  ) %>%
  # Format numbers with specific decimals for each column
  fmt_number(
    columns = vars(a_LER),
    decimals = 1
  ) %>%
  fmt_number(
    columns = vars(relative_crop_yield, relative_energy_yield),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(land_loss),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(mean_dry_weight),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(ELECTRICITY_OUTPUT_MWH_HA_YR),
    decimals = 0
  ) %>%
  # Adjust the column widths
  cols_width(
    vars(PV_SETUP_2) ~ px(180),
    vars(a_LER) ~ px(100),
    vars(relative_crop_yield) ~ px(120),
    vars(relative_energy_yield) ~ px(120),
    vars(land_loss) ~ px(100),
    vars(mean_dry_weight) ~ px(120),
    vars(ELECTRICITY_OUTPUT_MWH_HA_YR) ~ px(150)
  ) %>%
  cols_label(
    PV_SETUP_2 = "PV Setup",
    a_LER = "LER (%)",
    relative_crop_yield = "Relative Crop Yield (%) ",
    relative_energy_yield = "Relative Energy Yield (%) ",
    land_loss = "Land Loss (%)",
    mean_dry_weight = "Mean Crop Yield (t/ha)",
    ELECTRICITY_OUTPUT_MWH_HA_YR = "Electricity Output (MWh/ha/yr)"
  ) %>%
  tab_source_note(
    source_note = html(" Relative Crop Yield is calculated based on Global Mean Crop Yield [Dry Weight] of 4.27 t/ha for Winter Wheat Grain<br> Relative Energy Yield is calculated based on the Simulated Reference Energy Output (GCR = 0.5) of 935 (MWh/ha/yr).")
    )

##################################################################################################################
# Customize the clover table
clover_table_global_mean <- clover_data_global_mean %>%
  mutate(a_LER = (a_LER * 100) - 100) %>%  # Convert a-LER to percentage
  filter(!c(PV_SETUP_2 == "REFERENCE")) %>%  # Exclude the relative_energy_yield row
  gt() %>%
  tab_header(
    title = "Grass-Clover (all cuts)"
  ) %>%
  # Format numbers with specific decimals for each column
  fmt_number(
    columns = vars(a_LER),
    decimals = 1
  ) %>%
  fmt_number(
    columns = vars(relative_crop_yield, relative_energy_yield),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(land_loss),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(mean_dry_weight),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(ELECTRICITY_OUTPUT_MWH_HA_YR),
    decimals = 0
  ) %>%
  # Adjust the column widths
  cols_width(
    vars(PV_SETUP_2) ~ px(180),
    vars(a_LER) ~ px(100),
    vars(relative_crop_yield) ~ px(120),
    vars(relative_energy_yield) ~ px(120),
    vars(land_loss) ~ px(100),
    vars(mean_dry_weight) ~ px(120),
    vars(ELECTRICITY_OUTPUT_MWH_HA_YR) ~ px(150)
  ) %>%
  cols_label(
    PV_SETUP_2 = "PV Setup",
    a_LER = "LER (%)",
    relative_crop_yield = "Relative Crop Yield (%) ",
    relative_energy_yield = "Relative Energy Yield (%) ",
    land_loss = "Land Loss (%)",
    mean_dry_weight = "Mean Crop Yield (t/ha)",
    ELECTRICITY_OUTPUT_MWH_HA_YR = "Electricity Output (MWh/ha/yr)"
  ) %>%
  tab_source_note(
    source_note = html(" Relative Crop Yield is calculated based on Global Mean Crop Yield [Dry Weight] of 5.32 t/ha for Grass-Clover<br> Relative Energy Yield is calculated based on the Simulated Reference Energy Output (GCR = 0.5) of 935 (MWh/ha/yr).")
    )
```

```{r}
grain_table_global_mean
clover_table_global_mean
```


```{r}
# Define the folder path where you want to save the images
folder_path <- "OUTPUT"

# Save the grain table as a PNG image
grain_table_file_name <- "grain_table_global_mean.png"
grain_table_output_path <- file.path(folder_path, grain_table_file_name)
gtsave(grain_table_global_mean, grain_table_output_path)

# Save the clover table as a PNG image
clover_table_file_name <- "clover_table_global_mean.png"
clover_table_output_path <- file.path(folder_path, clover_table_file_name)
gtsave(clover_table_global_mean, clover_table_output_path)
```



####################################################################################################################
COMBINED TABLE
##########################################################

```{r}
# Combine the data from both crops into one data frame
combined_LER_table <- bind_rows(
  grain_data_global_mean %>% mutate(Crop_Type = "Winter Wheat Grain"),
  clover_data_global_mean %>% mutate(Crop_Type = "Grass-Clover (all cuts)")
) %>%
  mutate(
    a_LER = (a_LER * 100) - 100  # Convert a-LER to percentage
  ) %>%
  filter(!c(PV_SETUP_2 == "REFERENCE")) %>%  # Exclude the reference rows
  select(PV_SETUP_2, Crop_Type, a_LER, relative_crop_yield, relative_energy_yield, land_loss, mean_dry_weight, ELECTRICITY_OUTPUT_MWH_HA_YR) %>%  # Reorder the columns
  gt() %>%
  tab_header(
    title = "LER and associated values for the two agrivoltaic setups at Foulum, Denmark"
  ) %>%
  # Format numbers with specific decimals for each column
  fmt_number(
    columns = vars(a_LER),
    decimals = 1
  ) %>%
  fmt_number(
    columns = vars(relative_crop_yield, relative_energy_yield),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(land_loss),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(mean_dry_weight),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(ELECTRICITY_OUTPUT_MWH_HA_YR),
    decimals = 0
  ) %>%
  # Adjust the column widths
  cols_width(
    vars(PV_SETUP_2) ~ px(180),
    vars(Crop_Type) ~ px(200),
    vars(a_LER) ~ px(100),
    vars(relative_crop_yield) ~ px(120),
    vars(relative_energy_yield) ~ px(120),
    vars(land_loss) ~ px(100),
    vars(mean_dry_weight) ~ px(120),
    vars(ELECTRICITY_OUTPUT_MWH_HA_YR) ~ px(150)
  ) %>%
  cols_label(
    PV_SETUP_2 = "PV Setup",
    Crop_Type = "Crop Type",
    a_LER = "LER (%)",
    relative_crop_yield = "Relative Crop Yield (%) ",
    relative_energy_yield = "Relative Energy Yield (%) ",
    land_loss = "Land Loss (%)",
    mean_dry_weight = "Mean Crop Yield (t/ha)",
    ELECTRICITY_OUTPUT_MWH_HA_YR = "Electricity Output (MWh/ha/yr)"
  ) %>%
  tab_source_note(
    source_note = html(" Relative Crop Yield is calculated based on Global Mean Crop Yield [Dry Weight] of 4.27 t/ha for Winter Wheat Grain and 5.32 t/ha for Grass-Clover<br> Relative Energy Yield is calculated based on the Simulated Reference Energy Output (GCR = 0.5) of 935 (MWh/ha/yr).")
  )

# Display the combined table
combined_LER_table

```

SIMILAT PLOT BUT ADJUSTED TO THE MANUSCRIPT

```{r}
# Combine the data from both crops into one data frame
combined_LER_table_modified <- bind_rows(
  grain_data_global_mean %>% mutate(Crop_Type = "Winter Wheat Grain"),
  clover_data_global_mean %>% mutate(Crop_Type = "Grass-Clover (all cuts)")
) %>%
  mutate(
    a_LER = a_LER  # Show LER as a decimal
  ) %>%
  filter(!grepl("REFERENCE", PV_SETUP_2)) %>%  # Exclude the reference rows
  select(PV_SETUP_2, Crop_Type, a_LER, relative_crop_yield, relative_energy_yield, 
         land_loss, mean_dry_weight, ELECTRICITY_OUTPUT_MWH_HA_YR) %>%  # Reorder the columns
  gt() %>%
  tab_header(
    title = "LER and associated values for the two agrivoltaic setups at Foulum, Denmark"
  ) %>%
  # Format numbers with specific decimals for each column
  fmt_number(
    columns = vars(a_LER),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(relative_crop_yield, relative_energy_yield),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(land_loss),
    decimals = 0
  ) %>%
  fmt_number(
    columns = vars(mean_dry_weight),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(ELECTRICITY_OUTPUT_MWH_HA_YR),
    decimals = 0
  ) %>%
  # Adjust the column widths
  cols_width(
    vars(PV_SETUP_2) ~ px(180),
    vars(Crop_Type) ~ px(200),
    vars(a_LER) ~ px(100),
    vars(relative_crop_yield) ~ px(120),
    vars(relative_energy_yield) ~ px(120),
    vars(land_loss) ~ px(100),
    vars(mean_dry_weight) ~ px(120),
    vars(ELECTRICITY_OUTPUT_MWH_HA_YR) ~ px(150)
  ) %>%
  cols_label(
    PV_SETUP_2 = "PV Setup",
    Crop_Type = "Crop Type",
    a_LER = "LER",
    relative_crop_yield = "Relative Crop Yield (%) ",
    relative_energy_yield = "Relative Energy Yield (%) ",
    land_loss = "Land Loss (%)",
    mean_dry_weight = "Mean Crop Yield (t/ha)",
    ELECTRICITY_OUTPUT_MWH_HA_YR = "Electricity Output (MWh/ha/yr)"
  ) %>%
  tab_source_note(
    source_note = html(" Relative Crop Yield is calculated based on Global Mean Crop Yield [Dry Weight] of 4.27 t/ha for Winter Wheat Grain and 5.32 t/ha for Grass-Clover<br> Relative Energy Yield is calculated based on the Simulated Reference Energy Output (GCR = 0.5) of 935 (MWh/ha/yr).")
  )

# Display the combined table
combined_LER_table_modified

```

SAVE MANUALLY BY EXPORTING PLOT FROM PLOT PANE WINDOW

```{r}
# Customize the `gt` table with specific width and font adjustments
combined_LER_table_modified_2 <- combined_LER_table_modified %>%
  tab_options(
    table.width = pct(100),      # Set width to 100% of output area
    table.font.size = px(12)     # Adjust font size as needed
  )

# Define the folder path where you want to save the images
folder_path <- "OUTPUT"

# Save the combined_LER_table_modified
table_file_name <- "combined_LER_table_modified_2.png"
output_path <- file.path(folder_path, table_file_name)
gtsave(combined_LER_table_modified_2, output_path)
```

AN EDITABLE EXCEL VERSION

```{r}
# Load necessary libraries
# library(dplyr)
# library(writexl)

# Combine the data from both crops into one data frame
combined_LER_table_data <- bind_rows(
  grain_data_global_mean %>% mutate(Crop_Type = "Winter Wheat Grain"),
  clover_data_global_mean %>% mutate(Crop_Type = "Grass-Clover (all cuts)")
) %>%
  mutate(
    a_LER = a_LER  # Show LER as a decimal
  ) %>%
  filter(!c(PV_SETUP_2 == "REFERENCE")) %>%  # Exclude the reference rows
  select(PV_SETUP_2, Crop_Type, a_LER, relative_crop_yield, relative_energy_yield, land_loss, mean_dry_weight, ELECTRICITY_OUTPUT_MWH_HA_YR)  # Reorder the columns

# Write the combined data to an Excel file
output_file_path <- "OUTPUT"
write_xlsx(combined_LER_table_data, output_file_path)

# Print a message to confirm the file was saved
cat("The combined LER table has been saved to:", output_file_path)

```












```{r}
# SAVE MANUALLY BY EXPORTING PLOT FROM PLOT PANE WINDOW



# # Define the folder path where you want to save the images
# folder_path <- "OUTPUT"
# 
# # Save the grain table as a PNG image
# combined_LER_table_file_name <- "combined_LER_table.png"
# combined_LER_table_output_path <- file.path(folder_path, combined_LER_table_file_name)
# gtsave(combined_LER_table, combined_LER_table_output_path)
```



































##########################################################
INDIVIDUAL PV_SETUP MEAN _OUTSIDE_PV YIELD AS 'OPEN-FIELD' REFERENCE
##########################################################

```{r}
# Create combined columns for relative yields and land loss

```


