---
title: "WINDROSE_HYPER_2023"
author: "M.K.K. Lindhardt"
date: "2024-09-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##############################################################################################################################
PREPARING SCRIPT
##############################################################################################################################


```{r}
# Remove all objects
rm(list = ls())
```

## Packages to be installed first

```{r Installing the pacman package, warning=FALSE}
# install.packages("pacman")
library(pacman)
```

## Installing at loading packages and libraries needed

```{r Loading other needed packages, warning=FALSE}
# Suppress warnings while loading/installing packages
suppressWarnings({
  
  # Load only necessary packages using pacman::p_load
  pacman::p_load(
    conflicted,    # Manage conflicts between packages
    tidyverse,     # Data manipulation and visualization (includes dplyr, ggplot2, etc.)
    janitor,       # Data cleaning (cleaning column names)
    lubridate,     # Working with dates and times
    readr,         # Reading data (e.g., CSV files)
    readxl,        # Reading Excel data
    ggpubr,        # Publication-ready plots
    openair,       # Analyzing air quality and meteorological data
    grid,          # Low-level graphics system
    gridExtra,     # Arrange multiple plots
    png,           # Reading PNG images
    magick         # Image manipulation (used for combining and annotating images)
  )

  # Conditionally load other packages if specific functions are used
  if ("fuzzyjoin" %in% ls()) pacman::p_load(fuzzyjoin)  # For fuzzy joining
  if ("broom.mixed" %in% ls()) pacman::p_load(broom.mixed)  # For mixed model diagnostics
  if ("ggplot2.windrose" %in% ls()) pacman::p_load(ggplot2.windrose)  # For windrose plots

})

###############################################################################################
# Set preferences for conflicting functions

conflict_prefer("locale", "readr")
conflict_prefer("stamp", "lubridate")

conflict_prefer("filter", "dplyr")
conflict_prefer("group_by", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("arrange", "dplyr")
```


################
## STEP X
##############################################################################################################################
## REVIWEING CODE AND GRAPHS FOR FIGURES FOR COMMON PAPER aka 'MARTA PAPER'

## MARYAM'S CODE - ADAPTED
##############################################################################################################################

########################################################################################
IMPORT DATA
########################################################################################

```{r}
# Control reference station
control_wind_data <- read_csv("DATA/MICRO_MET/Control_WS_WD.csv")
control_wind_data |>  glimpse()

# South-oriented fixed-tilted 
s_wind_data <- read_csv("DATA/MICRO_MET/South_oriented_WS_WD.csv")
s_wind_data |>  glimpse()

# Vertical
v_wind_data <- read_csv("DATA/MICRO_MET/Vertical_WS_WD.csv")
v_wind_data |>  glimpse()
```

########################################################################################
PREPARING DATA - CLEAN AND RESHAPE DATA
########################################################################################

###################################################
NOT RELEVANT HERE BUT
On the 30th April 2024. nest 4 swapped with 5
###################################################

```{r}
# Function to read and clean data
read_and_clean_data <- function(data) {
  data <- data %>%
    filter(!is.na(Windspeed) & !is.na(Winddir) & Windspeed != "" & Winddir != "")
  return(data)
}

# Read and clean each dataset
control_wind_data <- read_and_clean_data(control_wind_data)
s_wind_data <- read_and_clean_data(s_wind_data)
v_wind_data <- read_and_clean_data(v_wind_data)
```


########################################################################################
DATA EXPLORATION 
########################################################################################

```{r}
# Function to summarize data
summarize_data <- function(data, nest) {
  summary <- data %>% 
    dplyr::filter(Nest == nest) %>%
    dplyr::summarize(
      mean_WINDDIR = mean(Winddir, na.rm = TRUE),
      sd_WINDDIR = sd(Winddir, na.rm = TRUE),
      median_WINDDIR = median(Winddir, na.rm = TRUE),
      mean_WINDSPEED = mean(Windspeed, na.rm = TRUE),
      sd_WINDSPEED = sd(Windspeed, na.rm = TRUE),
      median_WINDSPEED = median(Windspeed, na.rm = TRUE),
      count = n(),
      .groups = 'drop'
    )
  return(summary)
}

# Summarize each dataset for each nest
control_summary <- summarize_data(control_wind_data, "0")

s_summary_n1 <- summarize_data(s_wind_data, "1")
s_summary_n2 <- summarize_data(s_wind_data, "2")
s_summary_n5 <- summarize_data(s_wind_data, "5")

v_summary_n3 <- summarize_data(v_wind_data, "3")
v_summary_n4 <- summarize_data(v_wind_data, "4")
v_summary_n6 <- summarize_data(v_wind_data, "6")

# Print summaries
cat("\nControl Summary:\n")
print(control_summary)
cat("\nSouth-oriented Fixed-tilted Summary N1:\n")
print(s_summary_n1)
cat("\nSouth-oriented Fixed-tilted Summary N2:\n")
print(s_summary_n2)
cat("\nSouth-oriented Fixed-tilted Summary N5:\n")
print(s_summary_n5)
cat("\nVertical Summary N3:\n")
print(v_summary_n3)
cat("\nVertical Summary N4:\n")
print(v_summary_n4)
cat("\nVertical Summary N6:\n")
print(v_summary_n6)
```

########################################################################################
PLOTTING WINDROSES
########################################################################################

```{r}
# Function to create windrose using openair
create_windrose_openair_nest <- function(data, nest) {
  windRose(data, 
           #type = 'month',
           ws = 'Windspeed', 
           wd = 'Winddir', 
           paddle = FALSE, 
           border = TRUE,
           ws.int = 1, 
           breaks = c(0, 0.5, 1, 2, 4, 6, 8, 10, 12),
           main = paste("Windrose for Nest", nest),
           key.position = "right",
           key.title = "Wind Speed (m/s)",
           annotate = TRUE,
           par.settings = list(fontsize = list(text = 12)),
           col = "YlOrRd",
           angle.scale = 45,
           grid.line.width = 0.5
  )
}
```

```{r}
# Subsets for Control dataset
control_wind_data_clean_n0 <- control_wind_data %>% filter(Nest == "0")

# Subsets for South-oriented fixed-tilted dataset
s_wind_data_clean_n1 <- s_wind_data %>% filter(Nest == "1")
s_wind_data_clean_n2 <- s_wind_data %>% filter(Nest == "2")
s_wind_data_clean_n5 <- s_wind_data %>% filter(Nest == "5")

# Subsets for Vertical dataset
v_wind_data_clean_n3 <- v_wind_data %>% filter(Nest == "3")
v_wind_data_clean_n4 <- v_wind_data %>% filter(Nest == "4")
v_wind_data_clean_n6 <- v_wind_data %>% filter(Nest == "6")
```


```{r}
# Create windrose plots for each subset
control_windrose_n0 <- create_windrose_openair_nest(control_wind_data_clean_n0, "0")

s_windrose_n1 <- create_windrose_openair_nest(s_wind_data_clean_n1, "1")
s_windrose_n2 <- create_windrose_openair_nest(s_wind_data_clean_n2, "2")
s_windrose_n5 <- create_windrose_openair_nest(s_wind_data_clean_n5, "5")

v_windrose_n3 <- create_windrose_openair_nest(v_wind_data_clean_n3, "3")
v_windrose_n4 <- create_windrose_openair_nest(v_wind_data_clean_n4, "4")
v_windrose_n6 <- create_windrose_openair_nest(v_wind_data_clean_n6, "6")

# View the plots
# control_windrose_n0
# 
# s_windrose_n1
# s_windrose_n2
# s_windrose_n5
# 
# v_windrose_n3
# v_windrose_n4
# v_windrose_n6
```




########################################################################################
COMBINED WINDROSES PER PV_SYSTEM
########################################################################################

```{r}
# Function to preprocess wind speed data
preprocess_wind_speed <- function(data) {
  data <- data %>%
    # Categorize wind speeds below 4 m/s as 0,
    mutate(Windspeed = ifelse(Windspeed < 4, 0, Windspeed))
  return(data)
}
```

```{r}
###############################################################################################################
# Combine data for CONTROL (nests 0)
control_data <- control_wind_data %>% 
  filter(Nest %in% c("0")) |> 
  select(-Nest)

control_data_combined <- preprocess_wind_speed(control_data) |> 
  # Remove wind speed <= 0
  filter(Windspeed != 0)

###############################################################################################################
# Combine data for PV_SYSTEM = SOUTH-ORIENTED (FIXED-TILTED) (nests 1, 2, and 5)
south_oriented_data <- s_wind_data %>% 
  filter(Nest %in% c("1", "2", "5")) |> 
  mutate(Nest = "1,2,5") |> 
  select(-Nest)

s_wind_data_combined <- preprocess_wind_speed(south_oriented_data) |> 
  # Remove wind speed <= 0
  filter(Windspeed != 0)

###############################################################################################################
# Combine data for PV_SYSTEM = VERTICAL (nests 3, 4, and 6)
vertical_data <- v_wind_data %>% 
  filter(Nest %in% c("3", "4", "6")) |> 
  mutate(Nest = "3,4,6") |> 
  select(-Nest)

v_wind_data_combined <- preprocess_wind_speed(vertical_data) |> 
  # Remove wind speed <= 0
  filter(Windspeed != 0)
```

```{r}
head(south_oriented_data)
```
```{r}
head(s_wind_data_combined)
```
```{r}
# Function to check for NA, NaN, and empty values in a dataset
check_missing_values <- function(data) {
  # Check for NA values
  na_count <- sum(is.na(data))
  
  # Check for NaN values
  nan_count <- sum(is.nan(data))
  
  # Check for empty values (assuming empty means "")
  empty_count <- sum(data == "", na.rm = TRUE)
  
  # Return a summary
  list(
    na_count = na_count,
    nan_count = nan_count,
    empty_count = empty_count
  )
}

x_missing <- check_missing_values(s_wind_data$Windspeed)
x_missing
```


########################################################################################
FINAL PLOTS WITH ANNOTATIONS
########################################################################################

```{r}
###############################################################################################################
# Annotations

windrose_y_axis <- c(
    paste("Frequency of counts by wind direction (%)")
)

###############################################################################################################
# Reference

custom_annotation_c_mean_wind <- c(
    paste("Mean wind speed: ", round(mean(control_wind_data$Windspeed, na.rm = TRUE), 2), "m/s")
  )

custom_annotation_c_calm <- c(
    paste("Calm conditions: ", round(sum(control_wind_data$Windspeed <= 4) / nrow(control_wind_data) * 100, 1), "%")
  )

###############################################################################################################
# South-oriented

custom_annotation_s_mean_wind <- c(
    paste("Mean wind speed: ", round(mean(s_wind_data$Windspeed, na.rm = TRUE), 2), "m/s")
  )

custom_annotation_s_calm <- c(
    paste("Calm conditions: ", round(sum(s_wind_data$Windspeed <= 4) / nrow(s_wind_data) * 100, 1), "%")
  )

###############################################################################################################
# Vertical

custom_annotation_v_mean_wind <- c(
    paste("Mean wind speed: ", round(mean(v_wind_data$Windspeed, na.rm = TRUE), 2), "m/s")
  )

custom_annotation_v_calm <- c(
    paste("Calm conditions: ", round(sum(v_wind_data$Windspeed <= 4) / nrow(v_wind_data) * 100, 1), "%")
  )

###################################################################################

```

```{r}
# Function to create windrose with custom annotations using ggplot2
create_combined_windrose <- function(data, pv_system) {
  windRose(data, 
                ws = 'Windspeed', 
                wd = 'Winddir', 
                paddle = FALSE, 
                border = TRUE,
                annotate = FALSE,
                statistic = "prop.count",
                ws.int = 1, 
                breaks = c(4, 6, 8, 12, 18, 20),
                main = paste("", pv_system),
                key.position = "right",
                key.title = "Wind Speed (m/s)",
           # Colors can be changed according to the system of choice
           # Reference 'open-field': PuBuGn / Greens
           # South-oriented: Blues
           # Vertical: Oranges
                col = "Oranges",
                angle.scale = 45,
                grid.line.width = 0.5,
                normalise = FALSE
  )
  
}
```


SAVE MANUALLY BY EXPORTING PLOT FROM PLOT PANE WINDOW

```{r}
# Create windrose plots for control, south-oriented, and vertical datasets

# STEP 1: MAKE PLOT
# SAVE MANUALLY BY EXPORTING PLOT FROM PLOT PANE WINDOW

###################################################################################

control_windrose <- create_combined_windrose(control_data_combined, 
                                             # Update function colors before plotting
                                             pv_system = "OPEN FIELD     " 
                                             )

###################################################################################

south_oriented_windrose <- create_combined_windrose(s_wind_data_combined, 
                                                    # Update function colors before plotting
                                                    "TILTED SOUTH-ORIENTED SYSTEM        " 
                                                    )

###################################################################################

vertical_windrose <- create_combined_windrose(v_wind_data_combined, 
                                              # Update function colors before plotting
                                              "VERTICAL SYSTEM       " 
                                              )

```

MANUALLY READ THE SAVED IMAGE PLOTS BACK INTO R

```{r}
# STEP 2: READ THE SAVED IMAGE PLOTS BACK INTO R

img_windrose_c <- image_read("./FIGURES/MICROCLIM/windrose_open_field.png")
img_windrose_s <- image_read("./FIGURES/MICROCLIM/windrose_south_oriented.png")
img_windrose_v <- image_read("./FIGURES/MICROCLIM/windrose_vertical.png")



# STEP 3: CREATE A GGPLOT OBJECT WITH THE IMAGE AND ADDING MY COSTUM ANNOTATIONS

###################################################################################
# Reference

img_windrose_c_anno <- ggplot() +
  annotation_custom(rasterGrob(img_windrose_c, width = unit(12,"cm"), height = unit(12,"cm"))) +
  annotate("text", x = 2, y = 0, label = custom_annotation_c_mean_wind, 
           hjust = 1, 
           vjust = 17, 
           size = 4, 
           colour = "darkgreen") +
  annotate("text", x = 2, y = 0, label = custom_annotation_c_calm, 
           hjust = 1.12, 
           vjust = 18, 
           size = 4, 
           colour = "darkgreen") +
  annotate("text", x = 2, y = 0, label = windrose_y_axis, 
           hjust = 0.6, 
           vjust = 17, 
           size = 5, 
           colour = "black") +
  theme_void()

###################################################################################
# South-oriented

img_windrose_s_anno <- ggplot() +
  annotation_custom(rasterGrob(img_windrose_s, width = unit(12,"cm"), height = unit(12,"cm"))) +
  annotate("text", x = 2, y = 0, label = custom_annotation_s_mean_wind, 
           hjust = 1, 
           vjust = 17, 
           size = 4, 
           colour = "darkgreen") +
  annotate("text", x = 2, y = 0, label = custom_annotation_s_calm, 
           hjust = 1.12, 
           vjust = 18, 
           size = 4, 
           colour = "darkgreen") +
  annotate("text", x = 2, y = 0, label = windrose_y_axis, 
           hjust = 0.6, 
           vjust = 17, 
           size = 5, 
           colour = "black") +
  theme_void()

###################################################################################
# Vertical

img_windrose_v_anno <- ggplot() +
  annotation_custom(rasterGrob(img_windrose_v, width = unit(12,"cm"), height = unit(12,"cm"))) +
  annotate("text", x = 2, y = 0, label = custom_annotation_v_mean_wind, 
           hjust = 1, 
           vjust = 17, 
           size = 4, 
           colour = "darkgreen") +
  annotate("text", x = 2, y = 0, label = custom_annotation_v_calm, 
           hjust = 1.12, 
           vjust = 18, 
           size = 4, 
           colour = "darkgreen") +
  annotate("text", x = 2, y = 0, label = windrose_y_axis, 
           hjust = 0.6, 
           vjust = 17, 
           size = 5, 
           colour = "black") +
  theme_void()
```

SAVE MANUALLY BY EXPORTING PLOT FROM PLOT PANE WINDOW (600 x 600)

```{r}
img_windrose_c_anno
img_windrose_s_anno
img_windrose_v_anno

# SAVE MANUALLY BY EXPORTING PLOT FROM PLOT PANE WINDOW (600 x 600)

# CARDINALS (N, S, E, W) ARE ADDED MANUALLY IN ADOBE Illustrator
```

```{r}
img_windrose_combined_final <- image_read("./FIGURES/MICROCLIM/windrose_figure_final_windrose_combined_figure_updated_col_windrose_combined_figure_windrose_combined_figure.png")

img_windrose_combined_final
```